---
title: "Some data stats for Brain data"
author: "XSun"
date: "2023-04-14"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
suppressMessages(library(RSQLite))
suppressMessages(library(ggplot2))
```

# Introduction

Wingo et al. (Nat Communication, 2022, PMID: 35882878) generated FUSION weights in brain tissue that include LASSO model. 

LASSO mode and saved in /project2/guiming/data_download/model_weights/Wingo_722_brain_protein_models

The original brain FUSION weights are in /project2/guiming/data_download/Wingo_NC_2022/shared_mechanism.pQTLs.fusion.WEIGHTS_unzip

The LD file can be found in
/project2/guiming/data_download/Wingo_NG_proteome_2021/LDREF.

**The total number of genes is 2934**

# Number of SNPs selected by LASSO

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.height=5, fig.width=5}

load("/project2/guiming/xsun/1.brain_wingo/data/wgts_stats.rdata")

dat <- as.data.frame(cbind(num_snp_lasso, num_snp_enet))

ggplot(dat, aes(x = num_snp_lasso)) + 
  geom_histogram() +
  labs(x = "# of SNPs selected by LASSO", y = "Count") +
  theme_bw() 

```


# Number of SNPs selected by ENET

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.height=5, fig.width=5}

ggplot(dat, aes(x = num_snp_enet)) + 
  geom_histogram() +
  labs(x = "# of SNPs selected by ENET", y = "Count") +
  theme_bw() 

```


# Comparing the number of snp selected by LASSO and ENET

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.height=5, fig.width=5}

ggplot(dat, aes(x = num_snp_enet, y = num_snp_lasso)) +
  geom_point() +
  xlab("# of SNPs selected by ENET") +
  ylab("# of SNPs selected by LASSO") +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_bw()

```


